Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-13 doc/main_jfm.tex
small fixes

We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
single elliptical particle suspended in a background shear flow (see \S
\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are zero
for a single particle. The angle of the ellipse's major axis coming from
the integral equation method was in complete agreement with the
theoretical, Jeffrey oribit time-course \cite{}.

@@

The particles in our setup do not abut but rather have small gaps due to
repulsive forces.  The gaps allow for some fluid flux across the JP
bilayer.  In membrane mechanics, aqueous flux is quantified the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant \cite{CHABANON,
qua-gan-you2021}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations. (\cite{Zgorski2019,denOtter2007})
\todo[inline]{Need a reference here}

>>>>

We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
single elliptical particle suspended in a background shear flow (see
\S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
zero for a single particle. The angle of the ellipse's major axis coming
from the integral equation method was in complete agreement with the
theoretical, Jeffrey orbit time-course (\cite{jef1922}).

@@

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer. In membrane mechanics, aqueous flux is quantified the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations. (\cite{Zgorski2019,denOtter2007})
